%!TEX TS-program = xelatex
\documentclass[]{jameel-cv}
\usepackage[backend=biber]{biblatex}
\addbibresource{bibliography.bib}

\begin{document}
\header{Jameel}{Haffejee}
       {Full stack Developer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    \href{mailto:jameel@haffejee.co.za}{jameel@haffejee.co.za}
    \href{http://runawaycoder.co.za}{http://runawaycoder.co.za}
    \href{http://github.com/rc1140}{http://github.com/rc1140}
  \section{languages}
    english
  \section{programming}
    {\color{red} $\varheartsuit$} JavaScript
    (node.js),go
    Python, C, Clojure, C\#
    ASP.Net, ExtJs
    CSS \& HTML
\end{aside}

\section{interests}

Data mining, development and deployment at scale, reverse engineering, development focused challenges and competitions.

\section{experience}

\begin{entrylist}
   \entry
    {2013 - now }
    {Chase Software}
    {Systems Developer}
    {\emph{Development of an in house application. Managing and mentoring team members. System deployment and infrastructure maintenance}}
   \entry
    {2011 - 20013}
    {Thinkst}
    {Researcher}
    {\emph{Research and proof of concept development. Full stack application design, development,deployment and monitoring.}}
  \entry
    {2009 - 20011}
    {Chase Software}
    {Systems Developer}
    {\emph{Maintenance and development on an in house application of advertising agencies.}}
  \entry
    {2007 - 2009}
    {Neotel}
    {Systems Developer}
    {\emph{Development of OPIX, an in house application used for reporting and assisting in the rollout of the neotel fiber network.}}
  \entry
    {2006 - 2007}
    {Vas-X}
    {Systems Developer}
    {\emph{Development of internal application for managing airtime voucher sales and distribution.}}
\end{entrylist}

\section{applications}

\begin{entrylist}
   \entry
    {2013}
    {Longtail}
    {\href{https://bitbucket.org/rc1140/longtail}{https://bitbucket.org/rc1140/longtail}}
    {A server side application to monitor IRC channels and respond to emails with a mail digest since the users last request.}
  \entry
    {2012}
    {Signal Noise}
    {\href{http://signalnoi.se}{signalnoi.se}}
    {A web application for news agencies that monitored social media networks to determine the most relevant stories for the news agency.}
  \entry
    {2011}
    {Con Collector}
    {\href{http://cc.thinkst.com}{cc.thinkst.com}}
    {A website for collecting stats and other information regarding security conferences.}
  \entry
    {2011}
    {Cr-Gpg}
    {\href{https://github.com/RC1140/cr-gpg}{https://github.com/RC1140/cr-gpg}}
    {A chrome extension to bring gpg encrytion to gmail.}
\end{entrylist}

\section{education}

\begin{entrylist}
  \entry
    {2012 - 2014}
    {Masters Degree, Computer and Information Systems Security}
    {Rhodes University}
    {Completed research in the area of antivirus and virus analysis}
  \entry
    {2006}
    {Information Systems Engineering}
    {CTI, Randburg}
    {Completed in record time, used the extra time to study extra course material while job hunting}
\end{entrylist}

\newpage

\section{publications}
\nocite{*}
\printbibliography[heading=none]

\section{talks}
\begin{entrylist}
   \entry
    {20014}
    {\href{https://speakerdeck.com/rc1140/testing-antivirus-engines-to-determine-their-effectiveness-as-a-security-layer}{Testing antivirus engines to determine their effectiveness as a security layer}}
    {ISSA}
    {}
  \entry
    {20011}
    {\href{https://speakerdeck.com/rc1140/mac-os-sandboxing}{OS X Sandboxing}}
    {Zacon}
    {}
  \entry
    {2010}
    {\href{https://speakerdeck.com/rc1140/powershell-what-every-haxor-needs-to-know}{Powershell.. what every hax0r needs to know}}
    {Zacon}
    {}
\end{entrylist}

\end{document}
